The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts

### 2020-05-07 write-up/covid-writeup.tex
SIR updates

\begin{document}
\title{The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts}
% \author{Walter Dempsey\thanks{Department of Biostatistics, University of Michigan, 1415 Washington Heights, U.S.A. E-mail: wdem@umich.edu}}
\maketitle

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[width = 0.4\textwidth]{../methods/figs/mem_heatmap_article.png}
\caption{Measurement-error data quality adjustment: relative frequency $f_1/f_0$ (x-axis) against odds ratio (y-axis) for $FP=0.15$ and $FN=0.10$. Color scaled so blue = $-6$, white = 0, and red = $6$.}
\vspace{-0.7cm}
\end{wrapfigure}

@@

@@

@@

@@

>>>>

\begin{document}
\title[The Hypothesis of Testing]{The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts}
% \author{Walter Dempsey\thanks{Department of Biostatistics, University of Michigan, 1415 Washington Heights, U.S.A. E-mail: wdem@umich.edu}}
\maketitle

@@

@@

\begin{wrapfigure}{r}{0.5\textwidth}
\centering
\includegraphics[width = 0.4\textwidth]{../methods/figs/mem_heatmap_article.png}
\caption{Measurement-error data quality adjustment: relative frequency $f_1/f_0$ (x-axis) against odds ratio (y-axis) for $FP=0.15$ and $FN=0.10$. Color scaled so blue = $-6$, white = 0, and red = $6$.}
\vspace{-0.3cm}
\end{wrapfigure}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{../methods/figs/sir_ratio.png}
  \caption{A subfigure}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{../methods/figs/sir_rt.png}
  \caption{A subfigure}
  \label{fig:sub2}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:test}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{../methods/figs/sir.png}
  \caption{A subfigure}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{../methods/figs/sir_rt_comparison.png}
  \caption{A subfigure}
  \label{fig:sub2}
\end{subfigure}
\caption{A figure with two subfigures}
\label{fig:test}
\end{figure}

@@

\[
\rho = .004 \Rightarrow \Delta = 0.035 \times \sqrt{\frac{f \cdot (1-f)}{\bar Y \cdot (1 - \bar Y) }} = 0.00224 \Rightarrow M =
\]
